Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-14 paper/case-study.tex

We have modeled the system architecture of the UAV in AADL.  It includes a Mission Computer for communicating with the ground station and generating flight plans, and a Flight Control Computer for UAV navigation.  The Mission Computer architecture model includes hardware components such as a processor, memory, and communication devices, as well as software.
%
The initial software architecture model (shown in Figure~\ref{fig:sw-initial}) contains drivers for communication with the Ground Station and Flight Control Computer, a Waypoint Manager component that provides flight plan coordinates to the Flight Control Computer, and the Flight Planner.  The Flight Planner is the open-source UxAS software developed by AFRL~\cite{uxas}. For this application, UxAS accepts three types of messages.  The \textit{Operating Region} message defines where the UAV can and cannot fly.  The \textit{Line Search Task} message contains a series of waypoints that the UAV should traverse.  The waypoints typically lie along some geographical feature of interest, such as a river or railway.  Note that the UAV may not be able to directly traverse the Line Search Task waypoints due to no-fly zone constraints specified in the Operating Region message.  Anytime after receiving the Operating Region and Line Search Task messages, a ground station can transmit an \textit{Automation Request} message, which instructs UxAS to generate a flight plan that satisfies these constraints.  UxAS passes the flight plan in an \textit{Automation Response} message to the Waypoint Manager.  Because the Flight Control Computer can only process a small number of waypoints at a time, the Waypoint Manager parcels a small number of waypoints corresponding to the current UAV position, and sends them to the Flight Control Computer over a serial connection via the UART Driver.

@@

% Describe attestation?

@@

>>>>

We have modeled the system architecture of the UAV in AADL.  It includes a Mission Computer for communicating with the ground station and generating flight plans, and a Flight Control Computer for UAV navigation.  The Mission Computer architecture model includes hardware components such as a processor, memory, and communication devices, as well as software.
%
The initial software architecture model (shown in Figure~\ref{fig:sw-initial}) contains drivers for communication with the Ground Station and Flight Control Computer, a Waypoint Manager component that provides flight plan coordinates to the Flight Control Computer, and the Flight Planner.  The Flight Planner is the open-source UxAS software developed by AFRL~\cite{uxas}.

For this application, UxAS accepts three types of messages.  The \textit{Operating Region} message defines where the UAV can and cannot fly.  The \textit{Line Search Task} message contains a series of waypoints that the UAV should traverse.  The waypoints typically lie along some geographical feature of interest, such as a river or railway.  Note that the UAV may not be able to directly traverse the Line Search Task waypoints due to no-fly zone constraints specified in the Operating Region message.  Anytime after receiving the Operating Region and Line Search Task messages, a ground station can transmit an \textit{Automation Request} message, which instructs UxAS to generate a flight plan that satisfies these constraints.  UxAS passes the flight plan in an \textit{Automation Response} message to the Waypoint Manager.  Because the Flight Control Computer can only process a small number of waypoints at a time, the Waypoint Manager parcels a small number of waypoints corresponding to the current UAV position, and sends them to the Flight Control Computer over a serial connection via the UART Driver.

@@

% Describe attestation? virtualization?

@@

The UAV and Ground Station software were deployed on ODROID XU4 boards and communicated with each other over Ethernet.  The AMASE flight simulator, representing the Flight Contol Computer was run on a Linux machine and connected to the UAV ODROID board via serial connection.  The UxAS implementation on the UAV was modified by adding malicious code that would prevent it from responding to Automation Requests or produce flight plans that would violate the operating region constraints.  In addition, some of the Line Search Task messages transmitted from the Ground Station contained malformed messages that would modify the UxAS behavior.

We performed an initial set of tests on the initial un-hardened system (Figure~\ref{fig:sw-initial}) to verify the effectiveness of the malicious code.  We repeated the tests on the hardened system and were able to demonstrate that our mitigations were successful.
